DINO Methods for Style Transfer

### 2022-04-19 paper/Paper.tex
added image

MS-COCO [cite] is used as the content dataset and WikiArt [cite] is used as the style dataset. In the training stage,
all the images are randomly cropped into a fixed resolution of 256 × 256, while any image resolution is supported at the test time. We used the Adam optimizer [cite] and a warm-up adjustment strategy [cite] is used. Our GPU is not as big as the one used in the original paper, so while we could not train with their batch size, we modified the learning rate decay, number of iterations trained, and gradient accumulation steps to mimic the original's training process of a batch size of 8 for 160,000 iterations. Gradients are also clipped to a maximum norm of 10 to prevent exploding gradients.

\subsection{Qualitative Evaluation}
In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image. But in both cases, certain details of the objects depicted in the content image are lost with experiment B being better at preserving features. For experiment A, we can see both the content and style losses decrease over time. Meanwhile, experiment B has a decrease style loss but its content loss first decreases and then increases before oscilating and staying overall the same.

@@

Finally, experiment E also failed. In early stages of the training, the model renders the content with many colored vertical strips and many features were lost. Eventually, the model started to output single-color images. We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.
\subsection{Comparisons with SOTA Methods}

>>>>

MS-COCO [cite] is used as the content dataset and WikiArt [cite] is used as the style dataset. In the training stage,
all the images are randomly cropped into a fixed resolution of 256 x 256, while any image resolution is supported at the test time. We used the Adam optimizer [cite] and a warm-up adjustment strategy [cite] is used. Our GPU is not as big as the one used in the original paper, so while we could not train with their batch size, we modified the learning rate decay, number of iterations trained, and gradient accumulation steps to mimic the original's training process of a batch size of 8 for 160,000 iterations. Gradients are also clipped to a maximum norm of 10 to prevent exploding gradients.

\subsection{Qualitative Evaluation}

\includegraphics[scale=0.35]{comparison}

In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image. But in both cases, certain details of the objects depicted in the content image are lost with experiment B being better at preserving features. For experiment A, we can see both the content and style losses decrease over time. Meanwhile, experiment B has a decrease style loss but its content loss first decreases and then increases before oscilating and staying overall the same.

@@

Finally, experiment E also failed. In early stages of the training, the model renders the content with many colored vertical strips and many features were lost. Eventually, the model started to output single-color images. We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.

\subsection{Comparisons with Other Methods}
